Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-06 wsdm-2017/source/paper.tex
Yo dawg, I know you like revisions so I revised your revisions.

We now propose the {\em partial trust model}:
a technique for modeling communication between any two nodes
in an arbitrary network as communication across a number of
independent, direct links,
each of which might be compromised by an adversary.
Two links are considered {\em independent} if they do not
share a single point of failure.
Rather than assuming that trust is infinitely transitive (as in webs of trust),
this model assumes that trust is transitive up to a fixed number of hops.
The level of trust transitivity enters the model as a parameter called the
{\em trust radius}.
Any paths longer than this radius will contain some untrusted links,
hence {\em partial trust}.
The benefit of the partial trust model is its ability to abstract
away the details of the network structure,
while quantifying the amount of structural redundancy that can be
utilized by fault tolerance schemes.

To apply the partial trust model to a network,
we begin with an undirected graph $G = (V,E)$,
with nodes representing individual agents
and with edges representing mutual trust relationships
between those agents.
We define a {\em trust radius} $h$ and assume that trust is transitive
up to $h - 1$ hops away.
In other words, the nodes $v$ and $w$ trust each other if the distance between
$v$ and $w$, $d(v,w)$ is less than $h$.
For a given node $v$,
we call the set of nodes that $v$ trusts the
{\em trusted neighborhood} $T_h(v)$,
and all nodes at exactly distance $h$ from $v$ the
{\em trust boundary} $B_h(v)$:
\beq
T_h(v) &=& \left\{ w \mid d(v,w) < h \right\} \\
B_h(v) &=& \left\{ w \mid d(v,w) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $v$,
but if compromised can entirely isolate $v$ from the rest of the network.

Using the above definitions, we now model communication between a
source $v$ (Alice) and a destination $w$ (Bob).
We assume that nodes trusted by {\em either} Alice or Bob will not
compromise the message.
In other words,
faults are assumed to occur only in the part of the network lying
between Alice and Bob's trust boundaries.
We call this part of the network the {\em untrusted region}.
Our goal is now to model the maximum number of independent paths a message
can take through the untrusted region.
This is exactly the problem of finding $\delta_{v,w,h}$: the max-flow/min-cut of
the graph after each trusted neighborhood has been
collapsed into a single vertex.
Each trust boundary forms a cut of the network and places an upper bound on the
min-cut:
\beq
\delta_{v,w,h} \leq \min\left( \mid B_h(v) \mid, \mid B_h(w) \mid \right).
\eeq
Equality holds when there are no bottlenecks within the untrusted region.
For reasonably decentralized networks, equality should hold for all
values of $h$.
The redundancy of the entire graph can be characterized by the minimum over
all vertex pairs:
\beq
\delta_h(V) \equiv \min_{v,w \in V} \delta_{v,w,h}.
\eeq
Thus, for any pair of nodes in the network, at least $\delta_h$ independent,
redundant paths can be contstructed between them.
While $\delta_h$ is a purely structural property of the network,
it places an upper bound on the effectiveness of any
redundancy-based fault tolerance scheme.
We will now describe such a scheme.

>>>>

We can allow for more realistic transitivity assumptions and incorporate
network structure into a trust model with one key insight:
even if no single path between a sender and receiver is fully trusted,
multiple copies of a message can be sent along different paths and compared
by the reciever to detect and correct errors.
However, in the presence of an attacker, there is only benefit in sending an
additional message along a path if that path does not share untrusted
single points of failure with any of the existing message paths
(otherwise, the adversary can compromise both messages
by causing a single fault).
We call paths that do not share any untrusted single points of failure
{\em independent}.
The maximum number of independent paths represents the effective redundancy that
can be utilized by any redundancy-based fault-tolerance scheme.
We now propose a method for quantifying the effective redundancy of a network
as a function of its structure and level of trust transitivity.
For the purpose of analyzing adversarial fault-tolerance,
this method allows a communication network
to be modeled as a set of virtual channels that directly
connect each node pair,
with each channel providing some level of redundancy.

We now specify the {\em partial trust model}.
We begin with an undirected graph $G = (V,E)$,
with vertices representing agents,
and with edges representing mutually trusted communication links.
Let $v \in V$ be an arbitrary sender (Alice)
and $w \in V$ be an arbitrary receiver (Bob).
We assume the presence of an adversary (Mal) who knows the
full structure of the network,
and who can compromise a fixed number of agents,
gaining complete control of their behavior,
as long as those agents are not trusted by either Alice or Bob.
We define a {\em trust radius} $h$ and that nodes $u$ and
$u^\prime$ trust each other if their distance is less than $h$.
For a given node $u$,
we call the set of trusted nodes its
{\em trusted neighborhood} $T_h(u)$,
and all nodes at exactly distance $h$ the
{\em trust boundary} $B_h(u)$:
\beq
T_h(u) &=& \left\{ u \mid d(u,u^\prime) < h \right\} \\
B_h(u) &=& \left\{ u \mid d(u,u^\prime) = h \right\}.
\eeq
The trust boundary $B_h$ plays an important role because these nodes are not
trusted by $u$,
but if compromised can entirely isolate $u$ from the rest of the network.
These trust assumptions imply that when Alice sends a message to Bob,
Mal can only cause faults in the set of nodes outside both of their trusted
neighborhoods: $V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.

Our goal is now to model the maximum number of independent paths a message
can take through the untrusted region.
This is exactly the problem of finding $\delta_{v,w,h}$: the max-flow/min-cut of
the graph after each trusted neighborhood has been
collapsed into a single vertex.
Each trust boundary forms a cut of the network and places an upper bound on the
min-cut:
\beq
\delta_{v,w,h} \leq \min\left( \mid B_h(v) \mid, \mid B_h(w) \mid \right).
\eeq
Equality holds when there are no bottlenecks within the untrusted region.
For reasonably decentralized networks, equality should hold for all
values of $h$.
The redundancy of the entire graph can be characterized by the minimum over
all vertex pairs:
\beq
\delta_h(V) \equiv \min_{v,w \in V} \delta_{v,w,h}.
\eeq
Thus, for any pair of nodes in the network, at least $\delta_h$ independent,
redundant paths can be contstructed between them.
While $\delta_h$ is a purely structural property of the network,
it places an upper bound on the effectiveness of any
redundancy-based fault tolerance scheme.
We will now describe such a scheme.
